Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-16 papers/integration/omm_integ.tex
Work in progress on Rev2 comments

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model. Fig.~\ref{brain_model} shows the layout of the
populations and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus \citep{robinson_eye_1972}.
% and frontal eye field?

>>>>

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model, \rvwt{of reflexive saccadic behaviour}.
%
\rvwt{Reflexive saccades are fast eye movements elicited by abrupt
changes in the peripheral visual scene (reflexive saccades can occur
also as a result of auditory and somatosensory stimuli, but these
modalities are ignored here are in \cite{cope_basal_2017}). A
reflexive saccade has a starting position defined by the initial
orientation of the eye and an end-point position in which the eye is
directed towards a new target. Regardless of the number of targets
within the visual scene, the brain must choose one location as the
end-point, because the eyes can only look in one direction at a
time. The functionality reproduced by the \ccg~model is `the selection
of the best target end-point for a reflexive saccade'. A competition
such as this between competing, incompatible movements is often
referred to as an \e{action selection}
problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}

\rvwt{It is thought that in vertebrates, the basal ganglia (BG) play
an important r\^ole in action selection
\citep{mink_basal_1996,graybiel_basal_1998,hikosaka_role_2000}.
The \ccg~model places the BG at the centre of the oculomotor system,
following the known anatomy of the region.  The BG receives excitatory
inputs directly from retinotopic regions of the cortex including the
frontal eye fields (FEF), supplementary eye fields (SEF), lateral
intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The BG
receives input indirectly from the superior colliculus, which also has
a retinotopic arrangement. The dorsolateral prefrontal cortex, which
participates in voluntary saccades
\citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
modelled because the model concerns reflexive rather than voluntary
eye movements. Several other regions of the brain that are associated
with eye movements are also omitted from the model. The early visual
processing stream in cortex, from V1, through to the LIP is subsumed
into a `sustained retinal' signal. The justification here is that the
model reacts to simple luminant targets and does not need to carry out
the feature extraction performed by these visual areas. The
supplementary eye fields are involved in the programming of
saccades \citep{} and memory guided saccades \citep{}. Lesions of SEF
do not affect visually guided saccades \citep{} and so the SEF is also
omitted from the model.
%
% Figure here is the ``macroscopic architecture'' one.
%
The
BG's output is inhibitory and shapes the build-up of activity in both
of these regions.
%
The \ccg~model adopts a `channel based' model from previous
work~\citep{redgrave_basal_1999,gurney_basal_2004}. Within the context
of the basal ganglia model, a `channel' is a sub-set of neurons which
are associated with an individual action. Each channel in BG loops back via
relays in the thalamus through cortex. Input into this
thalamo-cortical loop is
termed `salience'. Because it is a loop, input salience to the channel
may originate cortically or sub-cortically. The higher the salience of
the channel, the greater is the behavioural relevance of the
associated action.

In the oculomotor model, an action
corresponds to a distinct saccade end point. It can be seen that the
action space for reflexive saccade end points is therefore
continuous rather than descrete.}

Fig.~\ref{brain_model} shows the layout of the populations in the
brain model and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus \citep{robinson_eye_1972}.
% and frontal eye field?
